Ligeti, Stockhausen and Koenig:\\Aesthetics of Electronic Music

### 2015-09-13 manuscript.tex
Esthetics -> Aesthetics
Add introduction to aesthetic ideals section

\title{Logeti, Stockhausen and Koenig:\\Esthetics of Electronic Music}
\author{Tom Gurion}

@@

\section{Esthetic Ideals in Electronic Music}
\label{sec:esthetic_ideals_in_Electronic_music}

>>>>

\title{Ligeti, Stockhausen and Koenig:\\Aesthetics of Electronic Music}
\author{Tom Gurion}

@@

\section{Aesthetic Ideals in Electronic Music}
\label{sec:aesthetic_ideals_in_electronic_music}

In this section I analyze musical concepts as described in \textbf{written materials} of the three composers.
For each composer I analyze one written source:
for Ligeti, I analyze ``Ligeti in conversation'' --- an interview that was conducted by Peter Varnai in 1983 (\cite{varnai});
for Stockhausen, I analyze his 1962 paper ``The concept of unity in electronic music'' (\cite{stockhausen});
and for Koenig, I analyze his 1963 paper ``The Construction of Sound'' (\cite{koenig}).

This work deals with aesthetics of electronic music, hence the decision to choose these papers by Stockhausen and Koenig is trivial.
On the other hand, for Ligeti I choose a source with broader perspective, as he cannot be described as an electronic composer.
Varnai's interview of Ligeti presents a comprehensive set of ideas behind Ligeti's composition style, and I found it useful as a basis to comparisons of musical concepts.

Later in this section I will compare these ideas, and search for similarities and differences between them.
A unified understanding of the different ideas by the different composers will be used to analyze their music in the next section.
